---
title: "Historical"
author: "Laura Slavsky"
date: "11/25/2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(scales)
library(DT)
```


read in the data (Randy added 26 Nov 19)

```{r}
BpSForGraphs <- read_csv("BpSForGraphs.csv", 
    col_types = cols(X1 = col_skip(), X1_1 = col_skip(), 
        X1_2 = col_skip(), X1_3 = col_skip(), 
        X1_4 = col_skip()))
```



horizontal bar chart


```{r}
BPSdescend <- BpSForGraphs %>%
  group_by(GROUPVEG) %>%
  summarise(ACRES = sum(ACRES))


```



```{r}
g <- ggplot(BpSForGraphs, aes(GROUPVEG, ACRES)) +

   coord_flip() + 
  scale_y_continuous(labels=comma) +
  geom_col() +

    coord_flip() +
    scale_y_continuous(labels = comma) +
    geom_col()
g
```

Group by BPS name (from Randy's googling)

Randy modified to use "BpSForGraphs" as input...
```{r}
DescendVeg <- BpSForGraphs %>%
  group_by(GROUPVEG) %>%
  summarise(ACRES = sum(ACRES))
```


Put in descending order
```{r}
g <- ggplot(DescendVeg, aes(x = reorder(GROUPVEG, ACRES), y = ACRES)) +

   coord_flip() + 
  scale_y_continuous(labels=comma) +
  geom_col() 
  
g
```

## Draft Historical Groupveg plot
Rename Axes, put title & center it, & color, & remove legend, remove gridlines
```{r}
gBpSGroups <- ggplot(DescendVeg, aes(x = reorder(GROUPVEG, ACRES), y = ACRES, fill = GROUPVEG)) +

   coord_flip() + 
  scale_y_continuous(labels=comma) +
  geom_col() +
  
  scale_fill_manual(values = c("Hardwood" = "darkorchid4", "Riparian" = "blue", "Hardwood-Conifer" = "darkgoldenrod3", "Conifer" = "darkgreen")) +
  
  labs(title="Historical Group Vegetation for the State of MI", y="Acres", x="") +
  theme(legend.position="none", plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank())
 
gBpSGroups
```

reduce number of ecosystem types
```{r}
bps_chop <- BpSForGraphs[c(1:15),]
```



## BPS graph top 15: 

```{r}
top15 <- ggplot(bps_chop, aes(x = reorder(BPS_NAME, ACRES), y = ACRES, fill = BPS_NAME)) +

   coord_flip() + 
  scale_y_continuous(labels=comma) +
  geom_col() +
  
  labs(title="Forested Ecosystems of Michigan-Historical Amounts", y="Acres", x="") +
  theme(legend.position="none", 
        plot.title = element_text(hjust = 0.5), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) 

 
top15
```


Randy will step into Excel to fix floodplain issue (there are two in the current BpSForGraphs table=GRRRR)

```{r}
write.csv(BpSForGraphs, file = "BpSForGraphs.csv")
```



## Data Table for BpS (Using Randy's Code)

```{r}
datatable(BpSForGraphs,
          class = 'cell-border stripe',
          filter = 'top', 
          options = list(pageLength = 5, autoWidth = TRUE))
```



## Sunburst chart

```{r}
# libraries
library(treemap)
library(sunburstR)

# Load dataset from github
data <- read.table("https://github.com/rswaty/mi_forests/blob/master/BpSForGraphs.csv", header=T, sep=";")
data[ which(data$value==-1),"value"] <- 1
colnames(data) <- c("BPS_NAME", "GROUPVEG", "ACRES", "PERCENT")

# Reformat data for the sunburstR package
data <- data %>%
  filter(Continent != "") %>%
  mutate(path = paste(GROUPVEG, BPS_NAME, PERCENT, sep="-")) %>%
  dplyr::select(path, PERCENT)

# Plot
p <- sunburst(data, legend=FALSE)
```

got error: "Error in UseMethod("filter_") : 
  no applicable method for 'filter_' applied to an object of class "function""

original code I tried to adjust: 

# libraries
library(tidyverse)
library(treemap)
library(sunburstR)

# Load dataset from github
data <- read.table("https://raw.githubusercontent.com/holtzy/data_to_viz/master/Example_dataset/11_SevCatOneNumNestedOneObsPerGroup.csv", header=T, sep=";")
data[ which(data$value==-1),"value"] <- 1
colnames(data) <- c("Continent", "Region", "Country", "Pop")

# Reformat data for the sunburstR package
data <- data %>%
  filter(Continent != "") %>%
  mutate(path = paste(Continent, Region, Country, sep="-")) %>%
  dplyr::select(path, Pop)

# Plot
p <- sunburst(data, legend=FALSE)
p

and link to website: https://www.data-to-viz.com/graph/sunburst.html










